## Mapping a vector into a landsat image
========================================================

*things we need for this worksheet*

* Landsat raster image B10 
* vector data_2014_subset 

*Before we start writing our code, we need to do some preprocessing*

load your requiered workspace and libraries
```{r,message=FALSE}
library(sp)
library(raster)
library(rgdal)
library(RColorBrewer)
library(latticeExtra)
```

```{r,echo=FALSE, message=FALSE, results="hide"}
setwd("D:/UNI/Master/WS_14-15/Data_management/Fogo/")
raster <- raster("LC82100502014328LGN00_B3.tif")
vector <- readOGR("data_2014_subset1.shp", "data_2014_subset1")
vector_proj <- spTransform(vector, CRS(projection(raster)))
```

write a function for natural species, including the underlaying Landsat image, legend, colorramp for this vector natural species
```{r,}
NAT_MAP <- function (raster, vector){
vector_classes <- cut(vector@data$NAT, c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9))
vector_colors <- colorRampPalette(brewer.pal(9,"YlGn"))(9)

yat = seq(extent(raster)@ymin, 
                extent(raster)@ymax, length.out = 5)
xat = seq(extent(raster)@xmin, 
                extent(raster)@xmax, length.out = 5)


plt <- spplot(raster, col.regions = gray.colors(256),
              key = list(space = 'left', text = list(levels(vector_classes)), 
                         points = list(pch = 21, cex = 3, fill = vector_colors)),
              colorkey=list(space="bottom"),
              panel = function(...){
                panel.levelplot(...)
                panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3) 
              },
              scales = list(x = list(at = xat),
                            y = list(at = yat)))

orl <- spplot(vector, zcol = "NAT", col.regions = vector_colors) 
              
plt + as.layer(orl)
}
```

Run the main function
```{r, echo=TRUE, include=TRUE}
NAT_MAP (raster, vector_proj)
```

