## Mapping a vector into a landsat image
========================================================

*things we need for this worksheet*

* Landsat raster image B10 
* vector data_2014_subset 

*Before we start writing our code, we need to do some preprocessing*

load your requiered workspace and libraries
```{r,message=FALSE}
library(sp)
library(raster)
library(rgdal)
library(RColorBrewer)
library(latticeExtra)
library (grid)
```

```{r,echo=FALSE, message=FALSE, results="hide"}
setwd("D:/UNI/Master/WS_14-15/Data_management/Fogo/")
raster <- raster("LC82100502014328LGN00_B3.tif")
readvector <- readOGR("data_2014_subset1.shp", "data_2014_subset1")
vector <- spTransform(readvector, CRS(projection(raster)))
```

write a function for natural species, including the underlaying Landsat image, legend, colorramp for this vector natural species
```{r,}
NAT_MAP <- function (raster, vector,  gnbr=7, attr=3){
vector_classes <- cut(vector@data$NAT, c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9))

# Koordinatensystem des Rasters definieren mit einem siebener Grid
yat = seq(extent(raster)@ymin, 
                extent(raster)@ymax, length.out = 7)
xat = seq(extent(raster)@xmin, 
                extent(raster)@xmax, length.out = 7)

# Vekoren in Klassen einteilen und Farbschema auswählen 
# if(vector_colors == "default"){
    vector_colors <- colorRampPalette(brewer.pal(9,"YlGn"))(9)  
 # }
vector_classes <- cut(vector@data$NAT, seq(0, 9, length.out = 256))

  breaks <- quantile(raster, seq(0.0, 1.0, length.out = 256))
  colorkey_scale <- 1/breaks


# Erstellen des plots vom Raster mit Legend
#plt <- spplot(raster, col.regions = gray.colors(256),at=breaks, 
              #key = list(space = 'left', text = list(levels(vector_classes)), 
              
 #             colorkey=list(space="bottom"),
  ##            
    #          panel = function(...){
     #           panel.levelplot(...)
      #          panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3) 
       #       },
        #      scales = list(x = list(at = xat),
         #                   y = list(at = yat)))


# Erstelle den plot mit Legende des vectors (orl) und des Rasters (plt)
vector_colors <- colorRampPalette(brewer.pal(9,"YlGn"))(256)
vector_classes <- cut(vector@data$NAT, seq(0, 9, length.out = 256))

plt <- spplot(raster, col.regions = gray.colors(256), at = breaks,
       colorkey=list(space="right"),
       panel = function(...){
         panel.levelplot(...)
         panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3) 
         },
       scales = list(x = list(at = xat),
                     y = list(at = yat)))

orl <- spplot(vector, zcol = "NAT", col.regions = vector_colors, cuts=256, colorkey=T)




 
              
print (plt + as.layer(orl)
}
```

Run the main function
```{r, echo=TRUE, include=TRUE}
NAT_MAP (raster, vector, gnbr=7, attr =3)
```




downViewport(trellis.vpname(name = "figure")) 
vp1 <- viewport(x = -0.25, y = 1,
                height = 1, width = 1,
                just = c("centre", "top"),
                name = "key.vp") 
pushViewport(vp1) 
draw.colorkey(key = list(col = vector_colors, width = 2,
                          at = seq(0, 9, length.out = 256),
                          space = "left"), draw = TRUE)
# print out
plt + as.layer(orl)
