---
title: "W10-01"
author: "Jakob Schmidt"
date: "15.01.2015"
output: html_document
---
To use the libraries that are required you need to install them first

```{r,warning=FALSE,eval=TRUE,message=FALSE}
library(raster)
library(rgdal)
library(sp)
library(latticeExtra)
library(lattice)
```
After the libraries have been installed and loaded we will set our filepaths and load our data now.
As we only have a raster and a vector dataset we can simply read the files with the
raster package and the ogr packages respectively.

```{r,warning=FALSE,eval=TRUE,message=FALSE}
setwd("/home/jakob/Documents/master/dm/data/fogo_landsat_2014-11-24")
file.name<-"LC82100502014328LGN00_B10.tif"
landsat<-raster(file.name)
v.path<-setwd("/home/jakob/Documents/master/dm/data/fogo_field_survey_2014")
vector<-readOGR("data_2014_subset1.shp","data_2014_subset1")
```
After the set up of your data the data still needs to be projected.
We can use the spTransform module for that purpose to project the shapefile while the raster is already correctly projected.
```{r,warning=FALSE,eval=TRUE,message=FALSE}
vector<-spTransform(vector, CRS(projection(landsat)))
coverage<-vector
```
Finally the data is almost ready to be plotted with spplot(). 
For this purpose we create a function that creates all settings for our plot using
different modules like cut() for setting our colorclasses of the NDVI Image.
Creating a function allows us to use different datasets with the same properties of the plot.
```{r,warning=FALSE,eval=TRUE,message=FALSE}
  


#plotting function
map.plot<-function(coverage,landsat,gridnum=5,color="Reds",col.class=6,attribute="COVRG"){
  # Funktioniert so leider nur in R-CRAN
#   entry<-FALSE
#     while(entry==FALSE){
#       gridnum<-readline("Please submit your desired gridsize:")
#       gridnum<- ifelse(grepl("\\D",gridnum),-1,as.integer(gridnum))
#       if (gridnum>=0){
#         entry<-TRUE
#       }
#     }
  names<-colnames(coverage@data)  
  attribute_in<-coverage@data[,grep(attribute,names)]
  vector_classes <- cut(attribute_in, c(0, 20, 40, 60, 80, 100, 120))
  vector_colors <- colorRampPalette(brewer.pal(col.class,color))(col.class)
  min <- max(mean(getValues(landsat)) - sd(getValues(landsat)), 0)
  max <- mean(getValues(landsat)) + sd(getValues(landsat))
  
  breaks <- seq(min, max, length.out = 256)
  yat = seq(extent(landsat)@ymin, 
                  extent(landsat)@ymax, length.out = gridnum)
  xat = seq(extent(landsat)@xmin, 
                  extent(landsat)@xmax, length.out = gridnum)

  plt <- spplot(landsat, col.regions = gray.colors(256), at = breaks,
       key = list(space = 'left', text = list(levels(vector_classes)), 
                     points = list(pch = 21, cex = 2, fill = vector_colors)),
       colorkey=list(space="right"), 
       panel = function(...){
         panel.levelplot(...)
         panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3)
         },
       scales=list(x=list(at=xat),y=list(at=yat))
       )

  orl <- spplot(coverage, zcol = "COVRG", col.regions = vector_colors, 
              cuts = c(0, 20, 40, 60, 80, 100, 120))

  plt + as.layer(orl)
}
map.plot(coverage,landsat)
```
