---
title: "Markdown"
author: "Benjamin Schumacher"
date: "15.01.2015"
output: html_document
---

This is a Tutorial for writing a function in R. You may use any other code to try out functions. 
First it is useful to read some data into r to work with. In this specific case we use data from the Fogo field Survey and a Landsat image of December 2014. 


```{r, echo=TRUE}
inpath <- "/home/benjamin/Data_Management/Raster"
setwd(inpath)

#install.packages('sp')
#install.packages('RColorBrewer')
library(sp)
library(raster)
library(rgdal)
library(latticeExtra)
library(rgdal)

library(RColorBrewer)

#1
thermo.tif <- raster("LC82100502014328LGN00_B10.tif")
inpath <- "/home/benjamin/Data_Management/Vector"
setwd(inpath)
field <- readOGR("data_2014_subset1.shp", "data_2014_subset1")
field <- spTransform(field, CRS(projection(thermo.tif)))
vegetation <- field
```

After the datasets are saved in the variables we can write our function to plot it.
Generally a function follows this syntax:

NAME <- function(Variables){
Function itself
}

In our case we use a raster and a vector layer to plot. That's why we are using "raster" and "vector" as names for the variables. 


```{r, echo=TRUE}

a <- function (raster, vector){
vector_classes <- cut(vector@data$COVRG, c(0, 20, 40, 60, 80, 100, 120))
vector_colors <- colorRampPalette(brewer.pal(6,"Greens"))(6)
min <- max(mean(getValues(raster)) - sd(getValues(raster)), 0)
max <- mean(getValues(raster)) + sd(getValues(raster))

breaks <- seq(min, max, length.out = 256)
yat = seq(extent(raster)@ymin, 
                extent(raster)@ymax, length.out = 5)
xat = seq(extent(raster)@xmin, 
                extent(raster)@xmax, length.out = 5)



plt <- spplot(raster, col.regions = gray.colors(256), at = breaks,
       key = list(space = 'left', text = list(levels(vector_classes)), 
                     points = list(pch = 21, cex = 2, fill = vector_colors)),
       colorkey=list(space="right"),
       panel = function(...){
         panel.levelplot(...)
         panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3) 
         }
       )

orl <- spplot(vector, zcol = "COVRG", col.regions = vector_colors, 
              cuts = c(0, 20, 40, 60, 80, 100, 120))

plt + as.layer(orl)
}


```
When the code is implemented, we may use it now to plot our data.


```{r, echo=TRUE}
a(thermo.tif, vegetation)

```