---
title: "The how-to you always wanted"
author: "Lin Zhong"
date: "Thursday, January 15, 2015"
output: html_document
---
Today we learn how to write a function which visualizes a spatial point vector attribute over a constrast strechted raster image. We take the data of the survey 2014 in Fogo as an example. For this section, package sp,rgdal,raster,RColorBrewer, lattice and latticeExtra are request.

```{r,echo=FALSE,eval=FALSE,warning=FALSE}
library(sp)
library(rgdal)
library(raster)
library(RColorBrewer)
library(lattice)
library(latticeExtra)

setwd("D:/1_uni/Environment GeographyWS14-15/data management/w08/fogo_landsat_2014-11-24/")

```

Before we go to the core of today, we must firstly finish our prepare work^.^ Read the raster and shape file and adapt the projection as we did before after loading the packages we need.

```{r,eval=FALSE}

landsat <- raster("LC82100502014328LGN00_B10.tif")
vegetation <- readOGR("data_2014_subset1.shp", layer = "data_2014_subset1")
vegetation_utm<-spTransform(vegetation, CRS(projection(landsat)))

```

At the second step we reach the main part of today's content:write the function!

```{r}

map <- function(raster,vector){
  
  min <- max(mean(getValues(raster)) - sd(getValues(raster)), 0)
  max <- mean(getValues(raster)) + sd(getValues(raster))

  breaks <- seq(min, max, length.out = 256)
  
  yat = seq(extent(raster)@ymin, 
                extent(raster)@ymax, length.out = 5)
  xat = seq(extent(raster)@xmin, 
                extent(raster)@xmax, length.out = 5)

  vector_classes <- cut(vector@data$COVRG, 6)

  vector_colors <- colorRampPalette(brewer.pal(6,"Greens"))(6) 
  
  plt <- spplot(raster, col.regions = gray.colors(256), at = breaks,
       key = list(space = 'left', text = list(levels(vector_classes)), 
                     points = list(pch = 21, cex = 2, fill = vector_colors)),
       colorkey=list(space="right"),
       panel = function(...){
         panel.levelplot(...)
         panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3) 
         },
       scales = list(x = list(at = xat),
                     y = list(at = yat)))

  orl <- spplot(vector, zcol = "COVRG", col.regions = vector_colors)

  plt + as.layer(orl)

}

```

Call the function now

```{r,eval=FALSE}
map(landsat,vegetation_utm)

```

If you want to call the function anytime,you can save the function in a separat R file and then  just use source() command to call it out whenever you want!

```{r,echo=TRUE,eval=FALSE}
source("map.R")
map(landsat,vegetation_utm)
```

Hope you enjoy this time!
